Immutable Source-Mapped Abstract Syntax Tree:\ \\ A Design Pattern for Refactoring Engine APIs

### 2016-08-11 paper.tex
The C plugin now works.

\acmformat{Overbey, J. 2013. Immutable Source-Mapped Abstract Syntax Tree.}

@@

To perform this refactoring, the conditional expression must be reversed in
meaning and the contents of the \textit{if} and \textit{else} branches must be
interchanged. Changing the condition requires removing the \textit{not} and the 
redundant parentheses. The former is simple enough, but the latter requires 
knowledge of matching parentheses. Interchanging the branches similarly requires 
knowledge of the matching braces, the location of the \textit{if} and dangling 
\textit{else}, and the presence or absence of any statements that alter flow of 
control such as \textit{goto}. In essence, knowledge of the program's syntax is 
required.

@@

    \item \textit{Work with the ASTs in a functional style, where every edit
        returns a new AST.} So, a call to field.removeFromTree() would not
        change the existing AST, but rather it would return a new AST that has
        the given field omitted. When dealing with immutable data structures,
        functional programming may often be the natural solution. However,
        in the case of ASTs, a functional style risks reintroducing many of 
        the problems inherent to mutable trees. File location of nodes may
        be disrupted in the new tree, pointers to nodes in the original tree ma
        be rendered 
        irrelevant, semantic information may be invalidated, etc. Those are in
        addition to the difficulties of functional programming, such as memory
        consumption and copying, especially with very large ASTs. This is
        a valid refactoring API design pattern, but any implementation using 
        this variant must carefully consider these problems.

@@

%\section{Example}

>>>>

\acmformat{Overbey, J. and Worley, C. 2013. Immutable Source-Mapped Abstract 
Syntax Tree.}

@@

To perform this refactoring, the conditional expression must be reversed in
meaning and the contents of the \textit{if} and \textit{else} branches must be
interchanged. Changing the condition requires removing the \textit{not} and the 
redundant parentheses. The former is simple enough, but the latter requires 
knowledge of matching parentheses and, in more complex cases, knowledge of operator
precedence. Interchanging the branches similarly requires 
knowledge of the matching braces, the location of the \textit{if}, and presence
or absence of the dangling 
\textit{else}.  In essence, knowledge of the program's syntax is 
required.

@@

    \item \textit{Work with the ASTs in a functional style, where every edit
        returns a new AST.} So, a call to field.removeFromTree() would not
        change the existing AST, but rather it would return a new AST that has
        the given field omitted. When dealing with immutable data structures,
        functional programming may often be the natural solution. However,
        in the case of ASTs, a functional style risks reintroducing many of 
        the problems inherent to mutable trees. File location of nodes may
        be disrupted in the new tree, pointers to nodes in the original tree may
        be rendered 
        irrelevant, semantic information may be invalidated, etc. Those are in
        addition to the difficulties of functional programming, such as memory
        consumption and copying, especially with very large ASTs. This is
        a valid refactoring API design pattern, but any implementation using 
        this variant must carefully consider these problems.

@@
